Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-08-17 EMNLP-demo-paper/result.tex
change fig.-> figure

As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pair (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea." However, these two \emph{greens} modify different nouns, which potentially leads to the wrong prediction. The grammatical structure is visually shown in the form of the dependency tree.
%i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
However, the model does not have access to the syntactic information and mistakenly assumes the two \emph{greens} modify the same thing.
% (thus predict \emph{entailment}). 
%
To correct the mistake, we can edit the attention value and remove the align between these two ``greens" (see (c)(b)).
As expected, the prediction label is corrected (\emph{neutral}).

>>>>

As illustrated in Figure~\ref{fig:NLIexample}(a), the input sentence pair (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea." However, these two \emph{greens} modify different nouns, which potentially leads to the wrong prediction. The grammatical structure is visually shown in the form of the dependency tree.
%i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
However, the model does not have access to the syntactic information and mistakenly assumes the two \emph{greens} modify the same thing.
% (thus predict \emph{entailment}). 
%
To correct the mistake, we can edit the attention value and remove the align between these two ``greens" (see (c)(b)).
As expected, the prediction label is corrected (\emph{neutral}).

### 2018-08-17 EMNLP-demo-paper/system.tex
change fig.-> figure

\subsection{Attention Visualization}
As illustrated in Figures~\ref{fig:attentionVis}(a)(b), the most widely adopted visual encodings for attention are  bipartite graphs (a) and heatmaps (b). 
%
In the graph attention view (Fig.~\ref{fig:attentionVis}(a)), the edge thickness corresponds to the attention value of the word pairs. %The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
The graph view is suitable for highlighting the most dominant alignments. However, the edges may become cluttered if multiple attention values are high. 
The matrix attention view (Fig.~\ref{fig:attentionVis}(b)) resolves these issues, despite being more verbose and less efficient in highlighting the most dominant alignments. 
We also enable the linkage between highlighted actions in both views (see Fig.~\ref{fig:attentionVis}(a)(b), where one alignment relationship is highlighted).

>>>>

\subsection{Attention Visualization}
As illustrated in Figures~\ref{fig:attentionVis}(a)(b), the most widely adopted visual encodings for attention are  bipartite graphs (a) and heatmaps (b). 
%
In the graph attention view (Figure~\ref{fig:attentionVis}(a)), the edge thickness corresponds to the attention value of the word pairs. %The color of the rectangle text block encodes the sum of all edge values connected to it (darker shade of blues correspond to higher values).
The graph view is suitable for highlighting the most dominant alignments. However, the edges may become cluttered if multiple attention values are high. 
The matrix attention view (Figure~\ref{fig:attentionVis}(b)) resolves these issues, despite being more verbose and less efficient in highlighting the most dominant alignments. 
We also enable the linkage between highlighted actions in both views (see Figure~\ref{fig:attentionVis}(a)(b), where one alignment relationship is highlighted).
